Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
edit pass of web version, added new system limitation amongst other changes

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites. We provide example
  usage scenarios that showcase each of our design principles.
\end{abstract}

@@

Notice how the \emph{row-sibling constraint} simplifies the problem: row
candidates without siblings that return an element after \(s\) is
executed on them ((b1) in Figure~\ref{fig:algorithm}) have
\(n_{siblings}\) = 0, thus disqualifying them. Furthermore, a candidate
element \(n\) is only accepted as the row element if the row selector
\(n_{selector}\) associated with it only matches itself and elements
that are its direct siblings.

@@

For \emph{Generalization Limitation 1} shown in
Figure~\ref{fig:limitations}, without the constraint that row elements
have to be direct siblings, the row generalization algorithm could
determine the row selector to be \emph{.avenger} (elements with blue
border in Figure~\ref{fig:limitations}) because it matches the largest
number of parallel structures (has the largest \(n_{siblings}\)). While
this may be the correct result for the task of extraction, it is not for
the task of customization. The selector matches all rows across the two
tables so the sorting and filtering customizations could place rows in
the incorrect table and thereby distort what the tables represent.
Because of this, our system currently does not support such DOM
structures but we plan to explore the possibility of extracting multiple
tables from a website and joining them.

For \emph{Generalization Limitation 2} shown in
Figure~\ref{fig:limitations}, website contains one table of data in
which rows are made up of the alternating H1 and SPAN tags (elements
with blue border in Figure~\ref{fig:limitations}). For the task of
extraction, the DOM elements can be scraped using the shown classes to
output a table in which the values of the H1 tags form the first column
and the values of the SPAN tag form the second column. For the task of
customization, our system would need to know what the row boundaries
were in order for customizations such as sorting and filtering to work
as expected. In Wildcard, this can be done with a hand-coded adapter by
creating artificial row boundaries. In the above DOM structure, an
artificial row boundary could be created by representing a row as an H1
tag and the SPAN tag that immediately follows it. These artificial rows
would form a single unit which would not distort the website after a
sorting or filtering customization. We plan to explore how such
artificial row boundaries might be created via demonstration in order to
support these structures (which are not uncommon, and can be seen, for
example, in HackerNews).

@@

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018} and commercial tools like
import.io \citep{import.io}, dexi.io \citep{dexi.io}, Octoparse
\citep{octoparse} and ParseHub \citep{parsehub}. In web customization,
the creators of Vegemite \citep{lin2009}, a system for end-user
programming of mashups, reported that participants of its user study
thought ``it was confusing to use one technique to create the initial
table, and another technique to add information to a new column.'' This
hints at the need for both a unified environment and a unified workflow.

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-51}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automtation. In fact, only the automation script
that works on the scraped website data can be edited. If a user needs to
add a new column or repair an exisiting one in the table, they need to
re-demonstrate the columns and then re-run the automation script. One
exception to point out is import.io \citep{zotero-77} which allows users
to add new columns by demonstration and delete columns and
re-demonstrate them which could serve the purpose of repair.

@@

Editing by demonstration makes end-users first-class citizens in the
customization ecosystem. Because users interact with the scraped data
directly in the context of the website, it is easy to initiate the
scraping system in editing mode: the scraping system is simply booted up
using metadata stored with the scraping adapter to the state when the
demonstration was completed. Users that have gone through the creation
process will immediately realize what to do in order to extend or repair
the adapter. Users that have not gone through the creation process might
have a harder time but we provide visual clues (such as highlighting the
row to perform demonstrations from with a green border) and live
programming (immediately preview the results of demonstrations) that
serve as guides.

@@

In many programming-by-demonstration web scraping systems, users only
get \emph{full} feedback about the program's execution (generalization
and the scraped values) after providing all the demonstrations. This
means they cannot adjust their demonstrations in response to the
system's feedback as they demonstrate.

>>>>

  We have successfully used our system to create, extend and repair
  adapters by demonstration on a variety of websites and we provide
  example usage scenarios that showcase each of our design principles.
\end{abstract}

@@

Notice how the \emph{row-sibling} constraint simplifies the problem: row
candidates without siblings that return an element after \(s\) is
executed on them ((b1) in Figure~\ref{fig:algorithm}) have
\(n_{siblings}\) = 0, thus disqualifying them. Furthermore, a candidate
element \(n\) is only accepted as the row element if the row selector
\(n_{selector}\) associated with it only matches itself and elements
that are its direct siblings.

@@

For \emph{Generalization Limitation 1} shown in
Figure~\ref{fig:limitations}, without the constraint that row elements
have to be direct siblings, the row generalization algorithm could
determine the row selector to be \emph{.avenger} (elements with blue
border) because it matches the largest number of parallel structures
(has the largest \(n_{siblings}\)). While this may be the correct result
for the task of extraction, it is not for the task of customization. The
selector matches all rows across the two tables (elements with green
border) so the sorting and filtering customizations could place rows in
the incorrect table and thereby distort what the tables represent.
Because of this, our system currently does not support such layouts but
we plan to explore the possibility of extracting multiple tables from a
website and joining them.

For \emph{Generalization Limitation 2} shown in
Figure~\ref{fig:limitations}, website contains one table of data in
which rows are made up of the alternating H1 and SPAN tags (elements
with blue border). For the task of extraction, the DOM elements can be
scraped using the shown classes to output a table in which the values of
the H1 tags form the first column and the values of the SPAN tag form
the second column. For the task of customization, our system would need
to know what the row boundaries were in order for customizations such as
sorting and filtering to work as expected. In Wildcard, this can be done
with a hand-coded adapter by creating artificial row boundaries. In
\emph{Generalization Limitation 2}'s layout, an artificial row boundary
could be created by representing a row as an H1 tag and the SPAN tag
that immediately follows it. These artificial rows would form a single
unit which would not distort the website after a sorting or filtering
customization. We plan to explore how such artificial row boundaries
might be created via demonstration in order to support these structures
(which are not uncommon, and can be seen, for example, in HackerNews).

Another major limitation of our system is our current lack of support
for scraping data loaded after the initial websites render as the user
scrolls. Hand-coded adapters can specify event listeners on the DOM to
re-execute the scraping code when new data is loaded as a user scrolls.
In future work, will we provide a mechanism for end-users to specify
when the adapter created via demonstration should re-execute its
scraping code in response to user scrolling. There is a similar
limitation for websites that have paged data but it is not clear how
suitable such pages are for customization to begin with.

@@

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018}and FlashExtract
\citep{le2014} and commercial tools like import.io \citep{zotero-77},
dexi.io \citep{dexi.io}, Octoparse \citep{zotero-83} and ParseHub
\citep{zotero-86}. In web customization, the creators of Vegemite
\citep{lin2009}, a system for end-user programming of mashups, reported
that participants of its user study thought ``it was confusing to use
one technique to create the initial table, and another technique to add
information to a new column.'' This hints at the need for both a unified
environment and a unified workflow.

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-51}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automtation demonstrations. In fact, only the
demonstrations used to perform automations on the scraped website data
can be edited. If a user needs to add a new column or repair an
exisiting one in the scraped data table, they need to re-demonstrate the
columns and then re-run the automation script. One exception to existing
editing models worth pointing out is import.io \citep{zotero-77}. It
allows users to add new columns by demonstration but it is not clear
whether deleting a column and re-demonstrating it could serve the
purpose of repair.

@@

Editing by demonstration makes end-users first-class citizens in the
customization ecosystem. Because users interact with the scraped data
through a unified environment directly in the context of the website, it
is easy to initiate the scraping system in editing mode: the scraping
system is simply booted up using metadata stored with the scraping
adapter to the state when the demonstration was completed. Users that
have gone through the creation process will immediately realize what to
do in order to extend or repair the adapter. Users that have not gone
through the creation process might have a harder time but we provide
visual clues (such as highlighting the row to perform demonstrations
from with a green border) and live programming (immediately preview the
results of demonstrations) that serve as guides.

@@

In many programming-by-demonstration web scraping systems
\citep[\citet{lin2009}]{chasins2018}, users only get \emph{full}
feedback about the program's execution (generalization and the scraped
values) after providing \emph{all} the demonstrations. This means they
cannot adjust their demonstrations in response to the system's feedback
as they demonstrate.
